\simname 2.0 User's Guide

### 2011-07-08 utils/doc/manual.tex
adaptiev routing stuff
git-svn-id: https://nocs.stanford.edu/cgi-bin/svn.cgi/booksim2.0/branches/indirect_adaptive_routing@3808 ce7aba0d-9f81-40a6-a495-cecae84b0515

% Copyright (c) 2007-2011, Trustees of The Leland Stanford Junior University
% All rights reserved.
% 
% Redistribution and use in source and binary forms, with or without 
% modification, are permitted provided that the following conditions are met:
% 
% Redistributions of source code must retain the above copyright notice, this 
% list of conditions and the following disclaimer.
% Redistributions in binary form must reproduce the above copyright notice, 
% this list of conditions and the following disclaimer in the documentation 
% and/or other materials provided with the distribution.
% Neither the name of the Stanford University nor the names of its contributors
% may be used to endorse or promote products derived from this software without
% specific prior written permission.
% 
% THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" 
% AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE 
% IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE 
% ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT OWNER OR CONTRIBUTORS BE 
% LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR 
% CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF 
% SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS 
% INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN 
% CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) 
% ARISING IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE 
% POSSIBILITY OF SUCH DAMAGE.

@@

The latest official release of the simulator can be checked out from our subversion (SVN) repository. Make sure a subversion client is installed on your machine; under UNIX, you can use the following command to check out a working copy:

\begin{verbatim}
svn co https://nocs.stanford.edu/cgi-bin/svn.cgi/booksim2.0
\end{verbatim}

The simulator files should now be in the \texttt{booksim2.0/trunk/src/} directory.
The simulator itself is written in C++ and has been specifically tested with the GNU G++ compiler (version $\ge3$).
The front end of the simulator uses LEX and YACC generated parser to process the simulator configuration file; however, unless you plan on making changes to the front end parser, LEX and YACC are not needed.
The \texttt{Makefile} should be edited so that the first few lines reflect the correct paths to the tools for your particular system.
The default \texttt{Makefile} should work on the Stanford Leland machines.
Type \texttt{make} to build the simulator.

>>>>

% Copyright (c) 2007-2010, Trustees of The Leland Stanford Junior University
% All rights reserved.
% 
% Redistribution and use in source and binary forms, with or without 
% modification, are permitted provided that the following conditions are met:
% 
% Redistributions of source code must retain the above copyright notice, this 
% list of conditions and the following disclaimer.
% Redistributions in binary form must reproduce the above copyright notice, 
% this list of conditions and the following disclaimer in the documentation 
% and/or other materials provided with the distribution.
% Neither the name of the Stanford University nor the names of its contributors
% may be used to endorse or promote products derived from this software without
% specific prior written permission.
% 
% THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS "AS IS" 
% AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE 
% IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE 
% ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT OWNER OR CONTRIBUTORS BE 
% LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR 
% CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF 
% SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS 
% INTERRUPTION) HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN 
% CONTRACT, STRICT LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) 
% ARISING IN ANY WAY OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE 
% POSSIBILITY OF SUCH DAMAGE.

@@

The latest official release of the simulator can be checked out from Booksim's sourceforge subversion (SVN) repository. Make sure SVN is installed on your machine and run the following command:
\begin{verbatim}
svn co https://booksim.svn.sourceforge.net/svnroot/booksim
\end{verbatim}

The simulator files should now be in the \texttt{booksim/trunk/src/} directory.
The simulator itself is written in C++ and has been specifically tested with GNU's G++ compiler (version $\ge3$).
The front end of the simulator uses LEX and YACC generated parser to process the simulator configuration file; however, unless you plan on making changes to the front end parser, LEX and YACC are not needed.
The \texttt{Makefile} should be edited so that the first few lines reflect the correct paths to the tools for your particular system.
The default \texttt{Makefile} should work on the Stanford Leland machines.
Type \texttt{make} to build the simulator.
